CTest Integration of Sikuli Automated GUI Testing

### 2011-06-20 Documentation/Article.tex
changed all "screen shot" to "screenshot"

\emph{Sikuli Script} automates anything you see on the screen without internal
API's support. Sikuli Script is a programming language that uses screen shot
images as variables and objects in order to automate graphical user interface
functions. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for acquiring and handling screen shot images and performing mouse,
keyboard actions.\\

In the \emph{Sikuli IDE}, the user can write scripts that include screen shot
thumbnails so they can visually track the functions of their code. The most
useful functions from Sikuli scripts are conveniently found as
buttons on the IDE. When using the IDE, Sikuli then saves a script in a
directory with a unique extension .sikuli. The directory consists of a python
script file (script file to be used by sikuli), an html file, and a list of all
the screenshot images used in the script.

@@

Figure~\ref{fig:SimpleExample} shows the Sikuli-IDE for version 0.10.2. On the
left-hand side menu is a list of commonly used Sikuli commands
like \emph{find}(), \emph{click}(), and \emph{type}(). The picture of
the camera within the parentheses indicates the screenshot input variable.
Clicking on any of these menu functions will automatically set up the Sikuli
screen shot mode, whereby the Sikuli-IDE disappears and what is on the screen at
that moment is available to capture by selecting a rectangular region of
interest. The function will then appear in the scripting domain with the snap
shot in parentheses as shown in Figure~\ref{fig:SimpleExample}. The user may
also type in the function and invoke the screen shot mode by clicking on the
camera in the top menu or by using a keyboard shortcut. The simple Sikuli script
example in Figure~\ref{fig:SimpleExample} will open gedit Text Editor, type a
message, and save the file.

>>>>

\emph{Sikuli Script} automates anything you see on the screen without internal
API's support. Sikuli Script is a programming language that uses screenshot
images as variables and objects in order to automate graphical user interface
functions. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for acquiring and handling screenshot images and performing mouse,
keyboard actions.\\

In the \emph{Sikuli IDE}, the user can write scripts that include screenshot
thumbnails so they can visually track the functions of their code. The most
useful functions from Sikuli scripts are conveniently found as
buttons on the IDE. When using the IDE, Sikuli then saves a script in a
directory with a unique extension .sikuli. The directory consists of a python
script file (script file to be used by sikuli), an html file, and a list of all
the screenshot images used in the script.

@@

Figure~\ref{fig:SimpleExample} shows the Sikuli-IDE for version 0.10.2. On the
left-hand side menu is a list of commonly used Sikuli commands
like \emph{find}(), \emph{click}(), and \emph{type}(). The picture of
the camera within the parentheses indicates the screenshot input variable.
Clicking on any of these menu functions will automatically set up the Sikuli
screenshot mode, whereby the Sikuli-IDE disappears and what is on the screen at
that moment is available to capture by selecting a rectangular region of
interest. The function will then appear in the scripting domain with the snap
shot in parentheses as shown in Figure~\ref{fig:SimpleExample}. The user may
also type in the function and invoke the screenshot mode by clicking on the
camera in the top menu or by using a keyboard shortcut. The simple Sikuli script
example in Figure~\ref{fig:SimpleExample} will open gedit Text Editor, type a
message, and save the file.
